\LARGE \bf Blockchain for routing correctness?

### 2018-07-20 paper.tex
fixed some diagram spacing issues
changes to intro

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Border Gateway Protocol does not guarantee correctness of routing updates. We define a given routing update for prefix X as \textit{correct} if for every AS in the AS-path of the update, the AS-path is still the most recent and valid for destination prefix X. This paper explores Blockchain-Merkle BGP (BM-BGP) which uses blockchain, indexed merkle trees, and bloom filters to provide correctness within the time frame of consensus in a chosen consensus protocol.

@@

\section{Introduction}
External gateway protocols such as BGP suffer from data availability problems. This paper explores whether blockchain can be used alongside BGPsec to provide a proof of correctness for routing updates. Specifically, this paper explores whether IP indexed merkle trees, blooms filters, and blockchain can be used to create common knowledge of route correctness to the relevant parties whenever a routing update is received.

Proof of correctness has 3 requirements: integrity, identity, and currentness. RPKI and BGPsec (when implemented) provide full integrity, full identity, and partial currentness. In BGPsec, there is a timestamp, however, it does not guarantee that a given routing update is the most recent one because updates can be withheld because of misconfigurations, new filters, or malicious ASes.

This paper proposes an algorithmic way to detect withholding of routes without using looking glass servers. Blockchain is used to create an ordering of routing tables and indexed merkle trees and bloom filters are used to ensure that routes are up-to-date in a scalable way.

@@

There are two shortcomings in this draft. First, the fact that BGP upgrades are so slow means that this protocol, even if fleshed out, would probably not ever be considered as an addition to BGP---the work is worthless or nearly worthless if only applicable to BGP. The goal in the future is see if similar ideas can be applied to the Bitcoin Lightning Network. Second, I (the author and researcher) am not confident in my ability to understand the severity of the data availability problem in BGP or any network relying on an external gateway protocol. I need guidance from an expert in BGP to (1) create a set of experiments to test the severity of data availability and (2) understand the current literature around data availability. Since it is one of the first iterations of this paper, I feel it is appropriate to add this disclaimer. I am much more confident in my understanding of blockchain than BGP. I am calling on those who are an expert in BGP to collaborate with me. Thank you.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Border Gateway Protocol does not guarantee correctness of routing updates. A given routing update for prefix X is defined as \textit{correct} if for every AS in the AS-path of the update, the AS-path is still the most recent and valid for destination prefix X. This paper explores Blockchain-Merkle BGP (BM-BGP) which uses blockchain, indexed merkle trees, and bloom filters to provide correctness within the time frame of consensus in a chosen consensus protocol.

@@

\section{Introduction}
External gateway protocols such as BGP suffer from data availability problems. This paper explores BM-BGP, which is an algorithmic way to detect the withholding of routes without using looking glass servers. Blockchain is used to create an ordering of routing tables and indexed merkle trees and bloom filters are used to ensure that routes are up-to-date in a scalable way. BM-BGP provides routing correctness which informally has three requirements: integrity, identity, and currentness. RPKI and BGPsec (when actually implemented) provide full integrity, full identity, and partial currentness. In BGPsec, there is a timestamp, however, it does not guarantee that a given routing update is the most recent one because updates can be withheld from misconfigurations, new filters, or malicious ASes.

@@

There are two shortcomings in this draft. First, the fact that BGP upgrades are so slow means that this protocol, even if proven beneficial (which this paper does not do), would probably not ever be considered as an addition to BGP---the work is worthless or nearly worthless if only applicable to BGP. The goal in the future is see if similar ideas can be applied to the Bitcoin Lightning Network. Second, I (the author and researcher) am not confident in my ability to understand the severity of the data availability problem in BGP or any network relying on an external gateway protocol. This paper defines the BM-BGP proposal, but does not rigorously test it. I need guidance from an expert in BGP to (1) create a set of experiments to test the severity of data availability and (2) understand the current literature around data availability. Since it is one of the first iterations of this paper, I feel it is appropriate to add this disclaimer. I am much more confident in my understanding of blockchain than BGP. I am calling on those who are an expert in BGP to collaborate with me. Thank you.
